MCLM parameters, interactive example

### 2024-05-14 apps/Graphical_representation_interactive.qmd
Adds latent trait plot in transformed basis

output$ts_original <- renderPlot({
})
output$ls_transformed <- renderPlot({
})
output$ts_transformed <- renderPlot({
})
```

>>>>

# Render scatter plot in transformed coordinates:
output$ts_original <- renderPlot({
})
output$ls_transformed <- renderPlot({

  # Constant objects:
  BREAKS <- -3:3

  # Compute grid lines:

  ## Basis vectors:
  basis_vec_1 <- transf_matrix()[, 1]
  basis_vec_2 <- transf_matrix()[, 2]
  basis_vec_1_norm <- basis_vec_1^2 |> sum() |> sqrt()
  basis_vec_2_norm <- basis_vec_2^2 |> sum() |> sqrt()

  ## Oblique grid lines:
  tan_vec_1 <- basis_vec_1[2] / basis_vec_1[1] # Angle tangent

  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline(intercept = 0, slope = tan_vec_1, linewidth = LINE_WIDTH) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = c(-3, 3),
      breaks       = -3:3,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     ),
     axis.line.y = 
    )
})
output$ts_transformed <- renderPlot({
})
```
